### 2020-06-24 Documents/ESA/sections/Intro.tex
minor mods in intro

    Swarm robotics bases its success upon the collaboration of many agents who contribute towards
    the overall success of the system \cite{Hamann2018}. The collaboration of many agents
    who share the same goal can give rise to behaviours that are far more complex than individual
    robots can achieve. The capacity for complexity is becoming increasingly important as robots are
    we are presented with ever more challenging tasks including: search and rescue, cleaning up
    space debris, and robotic assembly. Such tasks are beyond the capabilities of individual robots
    and so we must leverage the capacity for agents in a swarm to collectively achieve our
    goals. Fortunately, a growing subset of the Control Theory community have turned their attention
    towards this very problem and address the question: how does the dynamical behaviour of a
    population of agents change under the influence of control? Note that we use the term 'agent'
    loosely here, an agent can refer to anything from a simple particle \cite{Roy2017}
    to a complex robot \cite{Elamvazhuthi2019}. In answering this question, researchers have
    gained a stronger understanding of how a swarm may be controlled to achieve desired results.

@@

    Based on the successes of the swarm control and MARL communities, a natural question to ask is
    whether the promises of these disciplines may be unified. Such a combination would radically
    improve the capabilities of autonomous system. Ultimately such a system must be driven under the
    influence of control inputs to perform given tasks. Examples of this might be: forming around
    individual components of space debris and moving them to a desired location (e.g. a bin), or
    relocating to multiple areas in a disaster zone to provide immediate relief. For such tasks to
    be achieved in dynamic environments, which is typically the case, the system must be able to
    constantly adapt its approach and respond accordingly. Given these considerations, the problem
    may be stated as follows

    \begin{enumerate}
    	\item A population of robots is given a goal which must be achieved, which can often be
    	deconstructed into a set of smaller tasks, to be executed simultaneously. 
    	\item These are to be performed in a dynamic environment with obstacles present and where
    	the number of tasks, and their priorities may be in constant flux.
    	\item The agents in the system must, therefore, make decisions collectively which will in
    	the system achieving the given goals. Due to the dynamic quality of the problem, these
    	decisions may need to be evaluated online and in a decentralised fashion, as it may not be
    	possible for a centralised decision maker to communicate with all agents.
    	\item It is desirable, therefore, to control the dynamical behaviour of
    	a system composed of agents who learn and adapt through interactions with each other. In
    	addition, to ensure the safe operation of the system, properties such as state and control
    	constraints must be satisfied.
    \end{enumerate}

@@

>>>>

\fr{from the paragraph below it looks like we only deal with collaborative multi-agent systems. Is this really the case?}

    Swarm robotics bases its success upon the collaboration of many
    agents who contribute towards the overall goal of the system
    \cite{Hamann2018}. The collaboration of many agents who share the
    same goal give rise to behaviours that are far more complex
    than individual robots can achieve. The capacity for complexity is
    becoming increasingly important as robots are presented
    with ever more challenging tasks including: search and rescue,
    cleaning up space debris, and robotic assembly. Such tasks are
    beyond the capabilities of individual robots and so we must
    leverage the capacity for agents in a swarm to collectively
    achieve our goals. Fortunately, a growing subset of the Control
    Theory community has turned their attention towards this very
    problem and address the question: how does the dynamical behaviour
    of a population of agents change under the influence of control?
    Note that we use the term `agent' loosely here, an agent can refer
    to anything from a simple particle \cite{Roy2017} to a complex
    robot \cite{Elamvazhuthi2019}. In answering this question,
    researchers have gained a stronger understanding of how a swarm
    may be controlled to achieve desired results.

@@

    Based on the successes of the swarm control and MARL communities,
    a natural question to ask is whether the promises of these
    disciplines may be unified. Such a combination would radically
    improve the capabilities of autonomous system. Ultimately such a
    system must be driven under the influence of control inputs to
    perform given tasks. Examples of this might be: forming around
    individual components of space debris and moving them to a desired
    location (e.g.~a bin), or relocating to multiple areas in a
    disaster zone to provide immediate relief. For such tasks to be
    achieved in dynamic environments, which is typically the case, the
    system must be able to constantly adapt its approach and respond
    accordingly. Given these considerations, the problem may be stated
    as follows

    \begin{enumerate}
    	\item A population of robots is given a goal which must be
          achieved, which can often be deconstructed into a set of
          smaller tasks, to be executed simultaneously.
    	\item These are to be performed in a dynamic environment with
          obstacles present and where the number of tasks, and their
          priorities may be in constant flux.
    	\item The agents in the system must, therefore, make decisions
          collectively which \fb{will in the system achieving?} the given
          goals. Due to the dynamic quality of the problem, these
          decisions may need to be evaluated online and in a
          decentralised fashion, as it may not be possible for a
          centralised decision maker to communicate with all agents.
    	\item It is desirable, therefore, to control the dynamical
          behaviour of a system composed of agents who learn and adapt
          through interactions with each other. In addition, to ensure
          the safe operation of the system, properties such as state
          and control constraints must be satisfied.
    \end{enumerate}

@@

\fr{I would add here the paragraph describing the relevance to the CDT.}
